---
title: "Restaurant_Sales_Analysis_Report"
author: "Onyedikachukwu Okonkwo"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(ggplot2)

#Load and Clean Data

data <- read.csv("9. Sales-Data-Analysis.csv")
data_clean <- data %>%
  mutate(
    Date = dmy(Date), #convert Date to format
    Manager = str_squish(Manager), #remove extra spaces
    City = str_squish(City), 
    Product = str_squish(Product)
  )
rm(data)

#Create daily Sales Summary
daily_sales <- data_clean %>%
  group_by(Date) %>%
  summarize(
    total_sales = sum(Price * Quantity),
    num_orders = n()
  ) %>%
  mutate(
    day_of_week = wday(Date, label = TRUE)
  ) %>%
  arrange(Date)

#Create Sales averages by day of week
sales_average <- daily_sales %>%
  group_by(day_of_week) %>%
  summarize(mean_sales = mean(total_sales),
            mean_orders = mean(num_orders),
            average_cost_of_orders = mean_sales / mean_orders
            )

average_order <- sales_average %>%
  pull(mean_orders)

average_order_cost <- sales_average %>%
  pull(average_cost_of_orders)

#Create December Subset
december_sales <- daily_sales %>%
        filter(Date >= "2022-12-01")


```

**BOTTOM LINE UP FRONT**

This is predictive analysis based off the Resturant Sales Data from 9 November - 29 December. 

By analysis of the daily sales we can establish that Daily Sales will average $15K typically ranging between $14K-$16K

**ANALYSIS**

```{r analysis, echo=FALSE}
cat("Maximum single-day sales: $", max(daily_sales$total_sales), "\n\n")
cat("December Performance:\n")
cat("Average daily sales: $", mean(december_sales$total_sales), "\n")
print(summary(december_sales$total_sales))
```

**VISUALIZATION**

```{r pressure, echo=FALSE}
ggplot(daily_sales, aes(x= Date, y = total_sales)) +
  geom_line() +
  labs(
    title = "Sales Trend",
    x = "Date",
    y = "Total Sales",
  ) +
  theme_minimal() +
  scale_y_continuous(labels = scales::label_number(scale = 1/1000, suffix = "K")) +
  scale_x_date(date_breaks = "5 days", date_labels = "%d/%m")
```
**CONCLUSION**

By analysis of the daily sales we can establish that Daily Sales will average $15K typically ranging between $14K-$16K

